\tool

### 2018-04-17 paper/paper.tex
Implementation description more details added

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software dependency management tool for Java applications. We automatically inject \textsc{Error Prone} as a Maven plugin to a repository's project object model file (\textit{pom.xml}) and run the build process with the tool. \tool~builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications from the developer (head) to inspect differences. The base and head versions of the source code are tracked using the JGit Java API.\footnote{https://eclipse.org/jgit/}

@@

Code reviews between developers are a standard procedure of software engineering teams to improve code quality~\cite{CodeReviewingTrenches}. This practice also applies to GitHub projects, with many repositories requiring approval from another developer before changes can be merged into the main code base~\cite{PullRequestReview}. Our approach simulates peer code reviews by making recommendations for static analysis tools as a comment on pull requests and commits. Github allows users to make comments on specific lines of code in situ with the code changes. \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}. An example of a comment from \tool~is displayed in Figure \ref{fig:tool}.

>>>>

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software dependency management tool for Java applications. We clone the GitHub repository, automatically inject \textsc{Error Prone} as a Maven plugin to a repository's project object model file (\textit{pom.xml}), and then run the build process with the static analysis tool. \tool~builds both the original version of the code before the proposed changes (base) and the updated version of the repository with the modifications from the developer (head) to inspect differences in the \textsc{Error Prone} output. The JGit Java API\footnote{https://eclipse.org/jgit/} is used to clone projects and checkout the base and head versions of the code for our analysis.

@@

Code reviews between developers are a standard procedure of software engineering teams to improve code quality~\cite{CodeReviewingTrenches}. This practice also applies to GitHub projects, with many repositories requiring approval from another developer before changes can be merged into the main code base~\cite{PullRequestReview}. Our approach simulates peer code reviews by making recommendations for static analysis tools as a comment on pull requests and commits. Github allows users to make comments on specific lines of code in situ with the code changes. \tool~determines where to automatically make recommendation comments by converting the line number of the identified fix to the equivalent position in the diff file, or textual representation of code changes made in a commit or pull request, represented by the number of lines below the ``@@'' symbol in the header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}. Our system uses the jcabi Object Oriented GitHub API\footnote{http://github.jcabi.com/} to automatically comment on GitHub commits and pull requests. An example of a comment from \tool~is displayed in Figure \ref{fig:tool}.
